### 2017-07-15 background.tex
Minor edits

Traditional data enclaves hosted privately on-premise often have massive costs arising
from the cost of physical infrastructure to secure hardware, dedicated security and networking
teams to build and operate custom software and are limited in their ability to scale
compute capabilities in response to requirements. For a distributed research team that
focusses on large scale data analysis with highly sporadic nature an on-premise data enclave
is far too expensive and is lacks accessibility..A cloud hosted system would offer the scalability,
democratize access in terms of enabling anyone to host a secure data enclave and collaborate safely with a
distributed set of peers.

Cloud Kotta is a data-enclave designed to enable computation over sensitive data-sets
in a cost effective and secure manner. In prior work we've shown that Cloud Kotta offers
a scalable solution to match the compute needs of a distributed research network.
This model involved two classes of users: 1) the administrators who take on the role of managing
users, approving privileges and handling the transfer of data onto the data stores. 2) the analysts
who perform the role of developing analytical pipelines and running analyses on the data-sets.

On Cloud Kotta we currently archive over 10TB of compressed text data and in the past year
alone, analyses on the datasets consumed over 0.25M core hours. With a cloud hosted system
such as ours, designed to serve large scale computational analyses over large datasets,
the overheads of formal privacy techniques are financially impractical. More importantly
these techniques often don't lend themselves to arbitrary text data and complex analyses
on it. The system thus protects the hosted microdata by leveraging the strong security
guarantees of the cloud vendors infrastructure and by utilizing strong access control
models. The datasets come from various sources such as JSTOR, Web of Science, IEEE,
and UChicago grants database with varying sensitivities and legal requirements to
protect the microdata.

In data-science datasets with varying levels of sensitivity and can broadly be
categorized into three \cite{ist_dataclass} :
\begin{itemize}
\item \textbf{Public} : Datasets that are in the public domain and there is no
  reasonable expectation of sensitivity within it.
\item \textbf{Confidential}: Dataset contains private information and there is a legal/contractual obligation to control access and usage.
\item \textbf {Regulated}: Dataset contains sensitive data that can be widely damaging if disclosed.
  These are tightly controlled by government regulations. Eg HIPAA, SSNs etc
\end{itemize}

The workflow of an analyst on Cloud Kotta involves requesting access to a data-set, submitting analyses
tasks via the various interfaces to interrogate the data and tune the analyses until results are generated.
These results are available by requesting the UUID4 url of the submitted task and not tied to any user.
This was designed to allow for sharing of analyses codes and results, but this introduces the risk
of unintended, unapproved access to the generated results. More importantly since there is no disclosure
controls on the results generated, any sensitive data that makes it to the results can be exported.
This work extends our current security model and extends support for the most sensitive datasets
that require closer oversight on export of results as well as access.

>>>>

Traditionally data enclaves are hosted privately using on-premise infrastructure. As 
such they often require significant upfront investment (e.g. physical infrastructure) and reoccurring costs 
from the personnel required to operate the infrastructure as well as develop and maintain custom software. 
They are also often limited in their ability to scale
compute capabilities in response to requirements. In many cases an on-premise data enclave is far from ideal
when considering distributed research teams, large-scale data anlaytics, and highly sporadic
usage patterns common in data science. Instead, cloud hosted data enclaves offer scalability,
democratize access to capabilities, and can support distributed collaborations. 
 %terms of enabling anyone to host a secure data enclave and collaborate safely with a
%distributed set of peers.

\NAME is a data-enclave designed to enable computation over sensitive datasets
in a cost effective and secure manner. In prior work we've shown that \NAME offers
a scalable solution to match the compute needs of a distributed research network.
This model involved two classes of users: 1) the administrators who take on the role of managing
data, approving access, and handling the transfer of data onto the data stores; and 2) the analysts
who perform the role of analyzing and interrogating data via analyses pipelines.

\NAME currently manages over 10TB of compressed text data and in the past year
alone, its analyses have consumed over 0.25M core hours. With a cloud hosted system
such as \NAMENS, designed to enable large scale computational analyses over large datasets,
the overheads of formal privacy techniques are financially impractical. More importantly
these techniques often don't lend themselves to secure analysis of arbitrary text data. 
The system thus protects the hosted micro-data by leveraging the strong security
guarantees of the cloud vendor's infrastructure and by utilizing strong access control
models. The datasets managed in \NAME include JSTOR, Web of Science, IEEE,
and the UChicago grants database. Each has varying sensitivities and legal requirements to
protect the microdata.

\NAMENS's datasets can be broadly categorized into three \cite{ist_dataclass}:
\begin{itemize}
\item \textbf{Public} : Datasets that are in the public domain and there is no
  reasonable expectation of sensitivity.
\item \textbf{Confidential}: Datasets that contain private information and there is a legal/contractual obligation to control access and usage.
\item \textbf {Regulated}: Datasets that contain sensitive data that can be widely damaging if disclosed.
  These are tightly controlled by government regulations. Eg HIPAA, SSNs etc
\end{itemize}

The workflow of an analyst on \NAME involves requesting access to a dataset, submitting analysis
tasks via the various interfaces to interrogate the data and tune the analysis until results are generated.
These results are available by accessing a unique URL for the submitted task and are not tied to any user.
This was designed to allow for sharing of analysis codes and results, but it also introduces the risk
of unintended, unapproved access to the generated results. More importantly since there is no disclosure
controls on the results generated, any sensitive data that is included in results can be exported.
In this paper we describe how we have extended this security model to support the most sensitive datasets
that require stringent oversight with respect to data access access and export.
